%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Software Engineer and Solutions Architect} % Job title
    {Flexport Inc.} % Organization
    {Chicago, IL} % Location
    {June 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered company-wide taxonomy standardization tool impacting finance, cost-calculation, saving upwards of \textbf{\$ 4 Million} from cost leakage }
        % \item {Created dashboards to detect leakage of missing billing line items with an impact of \$ 500,000 per annum.}
        \item { Heavy experience in python services and cloud architecture resulted in leading initiative for a scalable, robust in-house CSV parsing service. }
        \item{Spearheaded Large Language Model initiative to automate ingestion of unstructured contract data requiring effective contextual awareness}
      \end{cvitems}
    }

  \cventry
    {Java Backend Engineer Co-op} % Job title
    {WHOOP Inc.} % Organization
    {Boston, MA} % Location
    {July 2021 - November 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led Financial Infrastructure overhaul involving \textbf{8 engineers} and \textbf{10 Million} rows of customer data over two months.}
        \item { Wrote and executed Project Proposals for upper management approval before partitioning tasks into Sprints + Epics for fellow engineers.}
        \item {Engineered Kafka Event Stream Consumers to process \textbf{1 million} daily health payloads for database replication.}
        % \item {Developed Stripe payment processing Web-hook technology to initiate cascading events on behalf of the customer after a purchase.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Python Developer Co-op and Part-time C++ Developer} % Job title
    {Scientific Systems Inc.} % Organization
    {Boston, MA} % Location
    {January 2021 - June 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated on middle-ware tech stack rehaul for improved performance and longevity.}
         \item {Revived a deprecated real-time analytic tool which decodes and visualizes \textbf{gigabytes} of autonomous drone flight data using multithreading.}
        \item {Dockerized the desktop tkinter GUI for easy adoption by U.S. Military Clients.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Full-Stack Software Engineer Intern} % Job title
    {Visual Labs Inc.} % Organization
    {Palo Alto, CA} % Location
    {May 2019 - August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Android and Web application features for production release.}
        \item {Invented bluetooth micro-controller to automatically trigger body-camera recordings.}
      \end{cvitems}
    }
%---------------------------------------------------------
%   \vspace{0.3cm}
%   \cventry
%     {Graduate-Innovation Award Recipient at RISE 2019} % Job title
%     {Cloud Computing Research under Professor David Kaeli PhD.} % Organization
%     {Boston, MA} % Location
%     {January 2019 – March 2020} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         % \item {Wrote scripts using the Message Passing Interface Protocol with Draper Labs }
%         \item {Co-discovered a rapid big-data parsing algorithm for \textbf{28-core} distributed computing system architectures.}
%       \end{cvitems}
%     }
%     \vspace{-0.3cm}

\end{cventries}
